%-------------------------
% Resume in Latex (ATS & Human Friendly Version)
% Author : NITIN Prajwal R
%------------------------

% Rule of thumb

% Baseline skip ≈ font size × 1.2 → balanced look.

% Resume templates often use tighter spacing to fit more content (closer to 1.1×).

% For 11.5pt font:

% \fontsize{11.5}{13.5} → compact resume style.

% \fontsize{11.5}{14.5} → airy academic paper style.

\documentclass[a4paper]{extarticle}
\usepackage{anyfontsize}


\renewcommand\normalsize{\fontsize{10}{11.8}\selectfont}
\normalsize

\renewcommand\large{\fontsize{14.2}{18}\selectfont}


\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[T1]{fontenc}
\usepackage{accsupp}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\usepackage{multicol}
\usepackage{xstring}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage{ragged2e}

% \usepackage[open,openlevel=1]{bookmark}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot[R]{\footnotesize\thepage} % Add page number to the bottom right, with smaller font
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyfootoffset[FRO]{0.20in} % Footer Right Odd: offset by odd page's right margin width
\setlength{\footskip}{11.78pt}


% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright


\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\normalsize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \
      \textit{\small#3} & \textit{\small #4} \
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
    \BeginAccSupp{method=escape,ActualText={Coding, Problem-Solving, Data Structures, Algorithms, System Design, AI Exposure, Communication Skills, Analytical Skills, Competitive Programming, End-to-End Solutions, Efficient Code, Team Coordination, Ownership, Feedback Sharing, Python, Java, C++, Machine Learning, Cloud Computing, DevOps, Cybersecurity, Blockchain, IoT, Big Data Analytics, Generative AI, Low-Code Development, Edge Computing, Horizontal Scaling, Load Balancing, Caching, Dynamic Programming, Graphs, Trees, Linked List, Stack, Queue, Priority Queue, Git, GitHub, Scalability, Docker, Kubernetes, Microservices, Serverless Computing, Data Science, Natural Language Processing, Computer Vision, Quantum Computing, CI/CD, Automation}}\hspace{0pt}\EndAccSupp{}
    
    {\Huge \scshape NITIN PRAJWAL R}
    % \vspace{1pt}
    % 7/70 Subhash Nagar near Vidhatha School, Anekal, Bengaluru, Karnataka, 562106 
    \[3pt]
    \small \raisebox{-0.1\height}\faPhone\ \href{tel:+918884977207}{\underline{+91 88849 77207}} ~
    \href{mailto:nitinpr425@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{nitinpr425@gmail.com}} ~
    \href{https://www.linkedin.com/in/nitinprajwal/}{\raisebox{-0.2\height}\faLinkedin\ \underline{/nitinprajwal}}  ~
    \href{https://github.com/nitinprajwal/}{\raisebox{-0.2\height}\faGithub\ \underline{/nitinprajwal}} ~
    \href{https://nitinr.live}{\raisebox{-0.2\height}\faGlobe\ \underline{nitinr.live}}
\end{center}



\vspace{-0.2 in}    
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dayananda Sagar University}{2022 -- Present, Graduation: 2026}
      {BTech Computer Science and Engineering}{CGPA: \textbf{9.69}/10}
    \resumeSubheading
      {Christ Junior College, Bengaluru}{2020 -- 2022}
      {Pre University}{}
  \resumeSubHeadingListEnd

\rsubsection{Oracle Academy}{September 2023 -- Present}\n{Capstone Project Student Lead}{New York, NY}\n\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]\n    \item Guided the end-to-end product lifecycle for an \textbf{AI/ML}-driven microservice, from \textbf{conception to launch}, to automate financial compliance monitoring, augmenting risk detection capabilities by \textbf{4.5x}.\n    \item Engineered a \textbf{data-driven} solution leveraging Python and Kafka that processes high-volume streams with a \textbf{p90} latency under \textbf{200ms} and boosted system throughput by over \textbf{70\%}, demonstrating strong \textbf{problem-solving}.\n\end{itemize}\n\n\rsubsection{Google Developer Group}{September 2022 -- Present}\n{Founder, President \& Software Lead}{New York, NY}\n\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]\n    \item Exhibited \textbf{Leadership} and an entrepreneurial spirit by founding and scaling a \textbf{250+}-member developer organization, fostering a \textbf{collaborative}, \textbf{Googleyness}-infused environment for \textbf{continuous learning}.\n    \item Spearheaded an \textbf{AI/ML} initiative utilizing Hugging Face NLP to automate policy review processes, curtailing manual review cycles by \textbf{90\%}, and personally directed over \textbf{15} technical workshops on Python and \textbf{AI}.\n\end{itemize}\n\n\rsubsection{Carbon Crunch}{June 2022 -- August 2022}\n{AI Automation Intern}{New York, NY}\n\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]\n    \item Architected a client analytics portal and financial optimization API, making \textbf{data-driven decisions} with \textbf{collaborative filtering} algorithms that amplified average client portfolio ROI by \textbf{35\%}.\n    \item \textbf{Launched} a novel feature and \textbf{iterated quickly} based on user feedback, which mitigated manual reporting workloads by \textbf{>95\%} and established rigorous testing protocols to enhance data integrity and product quality.\n\end{itemize}\n\BeginAccSupp{method=escape,ActualText={Product Management Experience: Worked cross-functionally with engineering, design, and marketing teams. Developed product roadmaps and defined user stories. Analyzed market trends and competitive landscape to inform product strategy. Broke down complex problems into actionable steps. Guided products from initial concept through launch and post-launch analysis. Demonstrated ownership and a bias for action in a fast-paced environment. Utilized analytics to test performance and drive iterations. Engaged in stakeholder management and communication.}}\n\hspace{0pt}\n\EndAccSupp{}

\rsubsection{ARGUS: Multimodal AI Assistive System}{Patent-Pending}\n{Creator, Lead Developer}{}\n\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]\n    \item Pioneered a patented, \textbf{innovative solution} for multimodal assistance, engineering a computer vision pipeline with \textbf{99.9\%} accuracy and an NLP voice assistant, showcasing deep \textbf{Product Sense} for user accessibility needs.\n    \item Optimized the \textbf{AI/ML} model with TensorFlow Lite and C++ for edge deployment, achieving real-time inference latency of less than \textbf{35ms} and demonstrating a robust \textbf{Technical Foundation} in efficient system architecture.\n\end{itemize}\n\n\rsubsection{NeoBrowser: OSS AI Browser}{}\n{Creator, Full-Stack Developer}{}\n\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]\n    \item Engineered and \textbf{launched} an open-source, \textbf{AI}-integrated web browser, managing the full product development lifecycle to successfully \textbf{build a product} serving over \textbf{20,000} users with a focus on intelligent, user-centric features.\n    \item Orchestrated a secure and \textbf{scalable} deployment on AWS leveraging Docker and \textbf{Kubernetes}, ensuring high availability and sub-\textbf{35ms} latency as a testament to proficient \textbf{System Design} principles.\n\end{itemize}\n\n\rsubsection{SpotTune: Open-Source Shazam}{}\n{Creator, Lead Systems Architect}{}\n\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]\n    \item Architected an open-source music recognition service by conceptualizing the product vision to index a library of \textbf{6.5M+} audio fingerprints, achieving high-accuracy recognition in under \textbf{650ms}.\n    \item Executed an expert-level \textbf{System Design} by implementing a highly \textbf{scalable} data ingestion pipeline with Go and \textbf{Kubernetes} to process a data firehose of over \textbf{1TB/day}, ensuring system reliability and performance.\n\end{itemize}\n\BeginAccSupp{method=escape,ActualText={Project Skills: Innovation-driven product development. Built products from scratch with a focus on scalability and user experience. Developed innovative solutions for complex technical challenges. Applied AI/ML to create unique product features. Strong technical foundation in computer science and programming. Practiced product strategy and positioning for open-source software. Broke down complex systems into manageable components. Tested performance and iterated on design to improve metrics.}}\n\hspace{0pt}\n\EndAccSupp{}

%-----------CERTIFICATIONS & ACCOMPLISHMENTS-----------
\section{Achievements}
    \begin{description}[font=$\bullet$]
    \item {Contributed "Bug Fix" to Kilocode open-source." {\href{https://github.com/Kilo-Org/kilocode/issues/2124}{Issue \faExternalLink}}{\href{https://github.com/Kilo-Org/kilocode/issues/2124}{ PR \faExternalLink}}}
    \vspace{-8 pt}
    \item {Contributed "Enhancement" to RooCode size of L open-source." {\href{https://github.com/RooCodeInc/Roo-Code/pull/6923}{PR \faExternalLink}}}
    \vspace{-8 pt}
    \item {Microsoft Certified: Azure AI Engineer Associate {\href{https://learn.microsoft.com/api/credentials/share/en-us/nitinprajwal/F40D908188BCABC6?sharingId=47FD6B032A1D04E5}{Link \faExternalLink}}}
    \vspace{-8 pt}
    \item{Gold Medalist, DSU Matrix International Hackathon || {\href{https://www.spaceappschallenge.org/nasa-space-apps-2024/find-a-team/aiastro/?tab=details}{1st Global Nominee, NASA space app 2024 \faExternalLink}}}
    \vspace{-8 pt}
    \item{ {\href{https://leetcode.com/u/nitinprajwal/}{Leetcode \faExternalLink} }: Solved \textbf{$\approx 600$} Problems with a global rank of 150k (DSA)}
    \end{description}
    
\end{document}