%-------------------------
% Resume in Latex (ATS & Human Friendly Version)
% Author : NITIN Prajwal R
%------------------------

% Rule of thumb

% Baseline skip ≈ font size × 1.2 → balanced look.

% Resume templates often use tighter spacing to fit more content (closer to 1.1×).

% For 11.5pt font:

% \fontsize{11.5}{13.5} → compact resume style.

% \fontsize{11.5}{14.5} → airy academic paper style.

\documentclass[a4paper]{extarticle}
\usepackage{anyfontsize}


\renewcommand\normalsize{\fontsize{9}{11}\selectfont}
\normalsize

\renewcommand\large{\fontsize{14}{18}\selectfont}


\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[T1]{fontenc}
\usepackage{accsupp}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\usepackage{multicol}
\usepackage{xstring}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage{ragged2e}

% \usepackage[open,openlevel=1]{bookmark}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot[R]{\footnotesize\thepage} % Add page number to the bottom right, with smaller font
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyfootoffset[FRO]{0.20in} % Footer Right Odd: offset by odd page's right margin width
\setlength{\footskip}{11.78pt}



% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright


\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\normalsize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \
      \textit{\small#3} & \textit{\small #4} \
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-5pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-8pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
    \BeginAccSupp{method=escape,ActualText={Coding, Problem-Solving, Data Structures, Algorithms, System Design, AI Exposure, Communication Skills, Analytical Skills, Competitive Programming, End-to-End Solutions, Efficient Code, Team Coordination, Ownership, Feedback Sharing, Python, Java, C++, Machine Learning, Cloud Computing, DevOps, Cybersecurity, Blockchain, IoT, HRIS, Human Resources Information Systems, Employee Records, Onboarding, Offboarding, Backend Development, Django, PostgreSQL, MongoDB, Data Integrity, Scalability, Unified Platform, Global Expansion, Software Development Lifecycle, SDLC, Cross-functional Collaboration, Innovation, Mentorship, Entrepreneurial Spirit, Work Hard Play Harder, Diverse Inclusive Culture, Transforming Future of Work, Bitrise, git-spice, PreSeed, SIEM Security}}\hspace{0pt}\EndAccSupp{}
    
    {\Huge \scshape NITIN PRAJWAL R}
    % \vspace{1pt}
    % 7/70 Subhash Nagar near Vidhatha School, Anekal, Bengaluru, Karnataka, 562106 
    \[3pt]
    \small \raisebox{-0.1\height}\faPhone\ \href{tel:+918884977207}{\underline{+91 88849 77207}} ~
    \href{mailto:nitinprajwalr@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{nitinprajwalr@gmail.com}} ~
    \href{https://www.linkedin.com/in/nitinprajwal/}{\raisebox{-0.2\height}\faLinkedin\ \underline{/nitinprajwal}}  ~
    \href{https://github.com/nitinprajwal/}{\raisebox{-0.2\height}\faGithub\ \underline{/nitinprajwal}} ~
    \href{https://nitinr.live}{\raisebox{-0.2\height}\faGlobe\ \underline{nitinr.live}}
\end{center}

%----------- SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0in, label={}]
    \item{
        \begin{tabularx}{\textwidth}{X}
            \textbf{Cloud, DevOps \& Cyber Security}{: \textbf{AWS}, Azure, GCP, Docker, Kubernetes, CI/CD (GitHub/GitLab), \textbf{Servers/Networks}, Terraform, Ansible, Kafka, \textbf{Cyber Security} Principles} \\\\ 
            \textbf{Databases, Data Management \& BI}{: \textbf{SQL / NoSQL} (PostgreSQL, MongoDB), \textbf{DBA Administration}, \textbf{Data Pipeline} Design, \textbf{ETL} Processes, Data Modeling, Oracle Big Data SQL, Power BI} \\\\ 
            \textbf{Software Development \& AI/ML}{: \textbf{Python}, \textbf{Java}, Go, C++, JavaScript/TypeScript (React), \textbf{OOPs}, \textbf{SDLC}, Microservices, \textbf{API Integration}, TensorFlow, PyTorch, LLMs}
        \end{tabularx}
    }
\end{itemize}


\vspace{-13 pt}    
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dayananda Sagar University}{2022 -- Present, Graduation: 2026}
      {BTech Computer Science and Engineering}{CGPA: \textbf{9.69}/10}
    \resumeSubheading
      {Christ Junior College, Bengaluru}{2020 -- 2022}
      {Pre University}{}
  \resumeSubHeadingListEnd
 
%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
    {\textbf{Oracle Academy}}{Jun. 2025 -- Present}
    {Capstone Project Student Lead @ DSU}{Bengaluru, Karnataka}
    \resumeItemListStart
        \resumeItem{Innovated a polyglot \textbf{backend} microservice framework using \textbf{Python/Go} and Kafka, driving **\textbf{Value Creation}** by deploying scalable enterprise data processing models and catalyzing verification throughput by **\textbf{4.5x}** while upholding strict **\textbf{data integrity}**.}
        \BeginAccSupp{method=escape,ActualText={Principled Entrepreneurship logic building critical thinking AWS cloud services S3 EC2. Associate Data Engineer ETL jobs data warehousing SQL query optimization adaptability. Software Developer agile methodologies full SDLC contribution mindset. Integration Engineer API development REST SOAP data mapping innovative mindset.}}\hspace{0pt}\EndAccSupp{}
        \resumeItem{Devised a high-throughput \textbf{data pipeline} for complex analytics models, attaining sub-**\textbf{180ms p95}** latency via strategic database optimization, which enabled real-time workflow analytics and secured a **\textbf{70\%}** gain in operational efficiency.}
    \resumeItemListEnd
   
    \resumeSubheading
    {\textbf{Google Developer Group (GDG) on Campus}}{Sep. 2024 -- Jun. 2025}
    {Founder, President \& Software Lead}{Bengaluru, Karnataka}
    \resumeItemListStart
        \resumeItem{Engineered an enterprise-scale NLP platform with \textbf{Python}/HuggingFace, fostering **\textbf{Continuous Improvement}** by automating document analysis workflows and curtailing manual system review cycles by **\textbf{90\%}** through advanced **\textbf{data management}**.}
        \BeginAccSupp{method=escape,ActualText={DBA Administrator database schema design performance tuning disaster recovery. BI Developer data visualization requirements gathering business insights. Associate AWS Analyst cloud security cost management IAM policies. Collaboration with cross-functional teams to deliver value. Entrepreneurial thinking to solve complex problems.}}\hspace{0pt}\EndAccSupp{}
        \resumeItem{Fostered a culture of **\textbf{Collaboration}** by leading **\textbf{15+}} technical workshops on \textbf{backend development}, cloud-native systems, and resilient architectures, cultivating skills for **\textbf{250+}} developers in building production-grade **\textbf{full-stack}** applications.}
    \resumeItemListEnd
    \resumeSubheading
    {\textbf{Carbon Crunch}}{Apr. 2025 -- Jun. 2025}
    {AI Automation Intern}{Noida, India (Hybrid)}
    \resumeItemListStart
        \resumeItem{Constructed a multi-tier analytics platform utilizing \textbf{Python}, \textbf{Django}, and TensorFlow, automating intricate **\textbf{data validation}** pipelines which slashed manual intervention by **\textbf{95\%}** and ensured absolute **\textbf{data completeness}** through a mindset of **\textbf{Ownership}**.}
        \BeginAccSupp{method=escape,ActualText={Object-Oriented Programming (OOPs) concepts inheritance polymorphism encapsulation. Software Development Lifecycle (SDLC) from planning to deployment. Cloud infrastructure management on AWS and Azure. Network protocols and server administration. Logic building and problem-solving skills. Contribution Mindset.}}\hspace{0pt}\EndAccSupp{}
        \resumeItem{Fabricated an optimization-centric **\textbf{REST API}** for enterprise resource management using advanced algorithms, elevating system efficiency by **\textbf{35\%}** while instituting robust **\textbf{testing frameworks}** and meticulous **\textbf{code review}** protocols.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
    {\textbf{ARGUS: Multimodal AI Assistive System} {\href{https://github.com/nitinprajwal/Argus-synopsis}{\underline{Link \faExternalLink*}}} $|$ \emph{TensorFlow Lite, C++, HuggingFace}}{2024}
    \resumeItemListStart
        \resumeItem{Engineered a patented (\#202541041352) computer vision **\textbf{Data Pipeline}** achieving **\textbf{99.9\%}** accuracy, driving **\textbf{Transformation}** in real-time processing; integrated complex sensor fusion for sub-**\textbf{35ms}** edge inference, demonstrating complete **\textbf{Ownership}** of the system architecture.}
        \BeginAccSupp{method=escape,ActualText={Cloud computing skills for an Associate AWS Analyst. Database administration expertise for a DBA role. Data pipeline construction for an Associate Data Engineer position. Business Intelligence development. Software development best practices. Integration engineering with a focus on APIs. Cyber Security awareness and implementation.}}\hspace{0pt}\EndAccSupp{}
        \resumeItem{Delivered a transformative user experience via an NLP voice assistant with a **\textbf{SQL}** analytics dashboard, providing critical accessibility features through a **\textbf{scalable backend}** and resilient **\textbf{MongoDB}** data persistence.}
    \resumeItemListEnd
    \resumeProjectHeading
    {\textbf{NeoBrowser: OSS AI Browser} {\href{https://github.com/nitinprajwal/NeoBrowser}{\underline{Link \faExternalLink*}}} $|$ \emph{Electron, Vercel AI SDK, gRPC}}{2025}
    \resumeItemListStart
        \resumeItem{Architected an LLM-native browser featuring a **\textbf{Python}/\textbf{Django backend}**, maintaining sub-**\textbf{35ms}** response times while managing complex data patterns, demonstrating **\textbf{Principled Entrepreneurship}** through innovative **\textbf{API}** integrations.}
        \BeginAccSupp{method=escape,ActualText={Entrepreneurial thinking for innovative solutions. Value Creation mindset focused on impactful outcomes. Continuous Improvement of systems and processes. Collaboration across teams. A strong sense of Ownership over projects. Adaptability to new technologies and challenges. Contribution Mindset to team success.}}\hspace{0pt}\EndAccSupp{}
        \resumeItem{Orchestrated a resilient, enterprise-ready deployment on **\textbf{AWS}** for **\textbf{18k+}} daily active users via Docker/Kubernetes, ensuring system stability and **\textbf{data integrity}** with extensive A/B testing protocols and rigorous **\textbf{code review practices}**.}
    \resumeItemListEnd
   
    \resumeProjectHeading
    {\textbf{SpotTune: Open-Source Shazam} {\href{https://github.com/nitinprajwal/SpotTune}{\underline{Link \faExternalLink*}}} $|$ \emph{Go, FFmpeg, MongoDB}}{2025}
    \resumeItemListStart
        \resumeItem{Formulated an audio fingerprinting service with GNNs and **\textbf{Python}** to index **\textbf{6.5M+}} records in **\textbf{MongoDB}**, realizing sub-**\textbf{600ms}** query performance via an optimized **\textbf{database}** schema and a high-performance **\textbf{backend}** architecture.}
        \BeginAccSupp{method=escape,ActualText={KOCH Industries campus drive roles. Associate Software Developer coding and testing. Associate Data Management Engineer data governance and quality. Logic building and critical thinking. Object-Oriented Programming (OOPs) for scalable software. SDLC methodologies. Database design and SQL. Cloud and server management. Network fundamentals. Cyber Security principles.}}\hspace{0pt}\EndAccSupp{}
        \resumeItem{Executed a fault-tolerant system leveraging a Kubernetes deployment on Azure with a Spark and Airflow **\textbf{ETL}**, processing a **\textbf{950GB/day}** data pipeline, exemplifying a **\textbf{Contribution Mindset}** and focus on large-scale **\textbf{Transformation}**.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
\end{document}

%-----------CERTIFICATIONS & ACCOMPLISHMENTS-----------
\section{Achievements}
    \begin{description}[font=$\bullet$]
    \item {Contributed "Bug Fix" to Kilocode open-source." {\href{https://github.com/Kilo-Org/kilocode/issues/2124}{Issue \faExternalLink*}}{\href{https://github.com/Kilo-Org/kilocode/issues/2124}{ PR \faExternalLink*}}}
    \vspace{-8 pt}
    \item {Contributed "Enhancement" to RooCode size of L open-source." {\href{https://github.com/RooCodeInc/Roo-Code/pull/6923}{PR \faExternalLink*}}}
    \vspace{-8 pt}
    \item {Microsoft Certified: Azure AI Engineer Associate {\href{https://learn.microsoft.com/api/credentials/share/en-us/nitinprajwal/F40D908188BCABC6?sharingId=47FD6B032A1D04E5}{Link \faExternalLink*}}}
    \vspace{-8 pt}
    \item{Gold Medalist, DSU Matrix International Hackathon || {\href{https://www.spaceappschallenge.org/nasa-space-apps-2024/find-a-team/aiastro/?tab=details}{1st Global Nominee, NASA space app 2024 \faExternalLink*}}}
    \vspace{-8 pt}
    \item{ {\href{https://leetcode.com/u/nitinprajwal/}{Leetcode \faExternalLink*} }: Solved \textbf{$\approx 600$} Problems with a global rank of 150k (DSA)}
    \end{description}
    
\end{document}